---
title: "Taylor Swift"
output: html_document
date: "2024-01-25"
---


```{r setup, include = FALSE}

library(tidyverse)
library(taylor)

knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```


## Example

There are three main data sets. The first is `taylor_album_songs`, which includes lyrics and audio features from the Spotify API for all songs on Taylor's official studio albums. Notably this excludes singles released separately from an album (e.g., *Only the Young*, *Christmas Tree Farm*, etc.), and non-Taylor-owned albums that have a Taylor-owned alternative (e.g., *Fearless* is excluded in favor of *Fearless (Taylor's Version)*). We stan artists owning their own songs.

```{r album-songs}
taylor_albulm_songs <- taylor_album_songs
```

You can access Taylor's entire discography with `taylor_all_songs`. This includes all of the songs in `taylor_album_songs` plus EPs, individual singles, and the original versions of albums that have been re-released as *Taylor's Version*.

```{r all-songs}
taylor_all_songs <- taylor_all_songs
```

Finally, there is a small data set, `taylor_albums`, summarizing Taylor's album release history.

```{r albums}
taylor_albums <- taylor_albums
```

```{r}

# Set up Spotify API access
client_id <- 'b5af36ff5bf1490b8e41060102108c5d'
client_secret <- '8b58d77e04024dfb92b775a989872556'

token <- httr::POST(
  url = "https://accounts.spotify.com/api/token",
  body = list(grant_type = "client_credentials"),
  authenticate(client_id, client_secret),
  encode = "form"
) |> httr::content("parsed")

artist_id = '06HL4z0CvFAxyc27GXpf02'  # Taylor Swift's Spotify artist ID



```

```{r}
# Install and load required packages
library(httr)
library(dplyr)


# Set up Spotify API access
client_id <- 'b5af36ff5bf1490b8e41060102108c5d'
client_secret <- '8b58d77e04024dfb92b775a989872556'

# Authenticate with Spotify API
token <- httr::POST(
  url = "https://accounts.spotify.com/api/token",
  body = list(
    grant_type = "client_credentials"
  ),
  authenticate(client_id, client_secret),
  encode = "form"
) |> httr::content("parsed")

# Get Taylor Swift's discography
artist_id <- '06HL4z0CvFAxyc27GXpf02'  # Taylor Swift's Spotify artist ID

albums <- httr::GET(
  url = paste0("https://api.spotify.com/v1/artists/", artist_id, "/albums"),
  add_headers(Authorization = paste0("Bearer ", token$access_token))
) |> httr::content("parsed")

# Extract track IDs
track_ids <- sapply(albums$items, function(album) album$uri)

# Get audio features for each track
audio_features <- lapply(track_ids, function(track_id) {
  httr::GET(
    url = paste0("https://api.spotify.com/v1/audio-features/", URLencode(track_id)),
    add_headers(Authorization = paste0("Bearer ", token$access_token))
  ) |> httr::content("parsed")
})

# Extract popularity scores
popularity_scores <- sapply(audio_features, function(features) features$popularity)

# Create a data frame
TS_popscore <- data.frame(TrackID = track_ids, PopularityScore = popularity_scores)

# Save the data frame to a CSV file
write.csv(TS_popscore, 'taylor_swift_popularity_scores.csv', row.names = FALSE)

```


```{r}

# Manually input the data for the new column
new_data <- c("103", "876", "999","103", "876", "999","103", "876", "999","103", "876", "999","103", "876", "999","103", "876", "999","103", "876", "999","103", "876", "999","103", "876", "999","103", "876", "999","103", "876", "999","103", "876", "999","103", "876", "999","103", "876", "999","103", "876", "999","103", "876", "999","103", "876", "999","103", "876", "999","103", "876", "999","103", "876", "999","103", "876", "999","103", "876", "999","103", "876", "999","103", "876", "999","103", "876", "999","103", "876", "999","103", "876", "999","103", "876", "999","103", "876", "999","103", "876", "999","103", "876", "999","103", "876", "999","103", "876", "999","103", "876", "999","103", "876", "999","103", "876", "999","103", "876", "999","103", "876", "999","103", "876", "999","103", "876", "999","103", "876", "999","103", "876", "999","103", "876", "999","103", "876", "999","103", "876", "999","103", "876", "999","103", "876", "999","103", "876", "999","103", "876", "999","103", "876", "999","103", "876", "999","103", "876", "999","103", "876", "999","103", "876", "999","103", "876", "999","103", "876", "999","103", "876", "999","103", "876", "999","103", "876", "999","103", "876", "999","103", "876", "999","103", "876", "999","103", "876", "999","103", "876", "999","103", "876", "999","103", "876", "999","103", "876", "999","103", "876", "999","103", "876", "999","103", "876", "999","103", "876", "999","103", "876", "999","103", "876", "999","103", "876", "999","103", "876", "999","103", "876", "999","103", "876", "999","103", "876", "999","103", "876", "999","103", "876", "999","103", "876", "999","103", "876", "999","103", "876", "999","103", "876", "999","103", "876", "999","103", "876", "999","103", "876", "999","103", "876", "999","103", "876", "999","103", "876", "999","103", "876", "999","103", "876", "999","103", "876", "999","103", "876", "999","103", "876", "999","103", "876", "999","103", "876", "999","103", "876", "999","103", "876", "999","103", "876", "999","103", "876", "999","103", "876", "999","103", "876", "999","103", "876", "999","103", "876", "999","103", "876", "999","103", "876", "999","103", "876", "999","103") 

# Add the new column directly to the existing data frame
taylor_all_songs$Streams <- new_data


```




